---
title: "ADA Final Project Data Cleaning"
author: "Mikayla Branz and Romario Smith"
date: "10/29/2020"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
    code_folding: "hide"
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE, message =FALSE, warning = FALSE)
```
# Bring in Data
Set up data frame:

- Import data from multiple CSV files
- Combine into one data frame
- Trim to remove extraneous variables
- Select only children 72 months and younger
```{r, import data, eval = FALSE}
#Install necessary packages 
pacman::p_load(readr,tidyverse, foreign, ggplot2, poliscidata, survey, MASS, funModeling, brant, dplyr, table1, car, DiagrammeR) 

#Set Working Directory
#setwd("C:/Users/Mikayla Branz/Documents/Grad School Work/Semester 5 Coursework/Advanced Data Analysis/Final Project")

#Use foreign to import .sav files. 
DHSload <- read.spss("ZAIR71FL.sav", use.value.label=TRUE, to.data.frame=TRUE)

#Select relevant variables:
DHS <- DHSload %>% 
dplyr::select(V781, V826A, V025, V012, V106, V190, V501, V208, V836, V525, V763A, V312, V394, V120, V121, V169A, V171A, V021, V022, V005)

#Verify
names(DHS)

#Rename variables
DHS <- DHS %>% 
  rename("HIVTest_Ever" = "V781", 
         "HIVTest_MonthsAgo" = "V826A", 
         "ResidenceType" = "V025", 
         "Age" = "V012", 
         "Education" = "V106", 
         "WealthIndex" = "V190",  
         "MaritalStatus" = "V501", 
         "Births_Last5Years" = "V208",  
         "SexPartners_Lifetime" ="V836",
         "FirstSex_Age" = "V525", 
         "STI_12Months" = "V763A", 
         "ContraceptiveMethod_Current" = "V312", 
         "HealthFacility_12Months" = "V394", 
         "Radio" = "V120", 
         "TV" = "V121", 
         "MobilePhone" = "V169A", 
         "InternetUse" = "V171A", 
         "Cluster" = "V021", 
         "Stratum" = "V022", 
         "Individual_Weight" = "V005")

#Select only women ages 15-24
DHS<-DHS %>%
  filter(Age >= 15 & Age<=24)
```

# Recode Exposure Variable: Residence Type
```{r}
#Check variable type
class(DHS$ResidenceType)

#Check distribution
summary(DHS$ResidenceType)

#Check for missing data
sum(is.na(DHS$ResidenceType))
#No missing values

#Reorder
DHS$ResidenceType<- factor(DHS$ResidenceType, levels = c("Rural", "Urban"))
```
# Recode Outcome Variable: HIV Testing Uptake
```{r}
#Check to ensure that people who never got an HIV test (HIVTest_Ever=0) did not report a number of Months on HIVTest_MonthsAgo. 
table(DHS$HIVTest_Ever, DHS$HIVTest_MonthsAgo)
#It looks consistent. No one in the "Don't know" category. 

#Recode HIV Testing uptake as Yes/No for within the last year. 

#Recode "2 or more years" as 25 so it will be easier to make into categories
DHS$HIVTest_MonthsAgo<-recode_factor(DHS$HIVTest_MonthsAgo,
                                     "Two or more years" = "25")

#Make HIV_MonthsAgo numeric so case_when can handle it
DHS$HIVTest_MonthsAgo<- as.numeric(DHS$HIVTest_MonthsAgo)
  
#Make categorical HIV test variable
DHS <- DHS %>% 
   mutate(HIVTest_LastYear = ifelse(HIVTest_Ever == "Yes" & HIVTest_MonthsAgo <12, "Yes", "No")) 

sum(is.na(DHS$HIVTest_LastYear))                                

#Make factor variable and check that it categorized variables correctly
DHS$HIVTest_LastYear<-as.factor(DHS$HIVTest_LastYear)
levels(DHS$HIVTest_LastYear)
DHS$HIVTest_MonthsAgo<- as.factor(DHS$HIVTest_MonthsAgo)
table(DHS$HIVTest_LastYear, DHS$HIVTest_MonthsAgo)
table(DHS$HIVTest_LastYear, DHS$HIVTest_Ever)
#Looks good!

```
# Fix other variables
## Age
```{r}
#Check missing values for Age variable
sum(is.na(DHS$Age))
#no missing values

#Check class for Age variable
class(DHS$Age)
#Numeric- Looks good!

DHS <- DHS %>% 
   mutate(Age_Cat = case_when(Age < 18 ~ "15-17", 
                              Age <21 & Age >=18 ~ "18-21", 
                              Age <=24 & Age >=21 ~ "21-24"))

class(DHS$Age_Cat)
#make factor variable
DHS$Age_Cat<-as.factor(DHS$Age_Cat)
#Summarize age variable
summary(DHS$Age_Cat)
```
## Education
```{r}
#Check missing values for education variable
sum(is.na(DHS$Education))
#no missing values

#Check class and levels for education variable
class(DHS$Education)
levels(DHS$Education)
summary(DHS$Education)

#Re-arrange into fewer categories
DHS <- DHS %>% 
   mutate(Education_Cat = case_when
                               (Education == "No education"
                                 | Education == "Primary" ~ "None or Primary",
                                Education == "Secondary" ~ "Secondary",
                               Education == "Higher" ~ "Higher"))

table(DHS$Education,DHS$Education_Cat)
#Looks good!

#Re-order levels
levels(DHS$Education_Cat)
 DHS$Education_Cat <- factor(DHS$Education_Cat, levels = c("None or Primary", "Secondary", "Higher"))
```
## Wealth Index
```{r}
#Check missing values for wealth variable
sum(is.na(DHS$WealthIndex))
#no missing values

#Check class and levels for wealth variable
class(DHS$WealthIndex)
levels(DHS$WealthIndex)
summary(DHS$WealthIndex)

#Re-arrange into fewer categories
 DHS <- DHS %>% 
   mutate(WealthIndex_Cat = case_when
                               (WealthIndex == "Poorest"
                                 | WealthIndex == "Poorer" ~ "Poor",
                              WealthIndex == "Middle" ~ "Middle",
                              WealthIndex == "Richer" |  
                              WealthIndex == "Richest" ~ "Rich"))

table(DHS$WealthIndex,DHS$WealthIndex_Cat)
#Looks good!

#Re-order levels
levels(DHS$WealthIndex_Cat)
 DHS$WealthIndex_Cat <- factor(DHS$WealthIndex_Cat, levels = c("Poor", "Middle", "Rich"))
```
## Marital Status
```{r}
#Check missing values for marital status variable
sum(is.na(DHS$MaritalStatus))
#no missing values

#Check class and levels for marital status variable
class(DHS$MaritalStatus)
levels(DHS$MaritalStatus)
summary(DHS$MaritalStatus)
#Looks good!

#Recategorize into fewer categories
DHS <- DHS %>% 
   mutate(MaritalStatus_Cat = case_when
                               (MaritalStatus == "Never in union" ~ "Never in union",
                                MaritalStatus == "Married" 
                                 | MaritalStatus == "Living with partner" ~ "Partnered",
                               MaritalStatus == "Widowed"
                                 | MaritalStatus == "Divorced"
                                 | MaritalStatus == "No longer living together/separated" ~ "Not partnered"))
                             
DHS$MaritalStatus_Cat<-as.factor(DHS$MaritalStatus_Cat)
table(DHS$MaritalStatus_Cat,DHS$MaritalStatus)
```
## Births in the last 5 years
```{r}
#Check missing values for births in the last 5 years variable
sum(is.na(DHS$Births_Last5Years))
#no missing values

#Check class and levels for births in the last 5 years variable

class(DHS$Births_Last5Years)
levels(DHS$Births_Last5Years)
summary(DHS$Births_Last5Years)


#Recategorize Births Variable

DHS <- DHS %>% 
   mutate(Births_Last5Years_Cat = case_when
                               (Births_Last5Years == "No births" ~ "No Births", 
                                 Births_Last5Years == "1" ~ "1 Birth",
                                 Births_Last5Years == "2"| Births_Last5Years == "3" ~ "2+ Births"))

DHS$Births_Last5Years_Cat<-as.factor(DHS$Births_Last5Years_Cat)
table(DHS$Births_Last5Years_Cat)

#Looks good!

#Re-level
DHS$Births_Last5Years_Cat<- factor(DHS$Births_Last5Years_Cat, levels = c("No Births", "1 Birth", "2+ Births"))
levels(DHS$Births_Last5Years_Cat)
```
## Lifetime sex partners
```{r}
#Check missing values for lifetime sex partners variable
sum(is.na(DHS$SexPartners_Lifetime))
class(DHS$SexPartners_Lifetime)
summary(DHS$SexPartners_Lifetime)
#978 missing values (match with "not had sex" from "FirstSex_Age)

#Check class and levels for lifetime sex partners variable
class(DHS$SexPartners_Lifetime)
levels(DHS$SexPartners_Lifetime)
#Change "NA" values to 0 since these cases did not have sex
DHS$SexPartners_Lifetime<-as.character(DHS$SexPartners_Lifetime)
DHS$SexPartners_Lifetime[is.na(DHS$SexPartners_Lifetime)]= 0
DHS$SexPartners_Lifetime<-as.factor(DHS$SexPartners_Lifetime)
levels(DHS$SexPartners_Lifetime)
summary(DHS$SexPartners_Lifetime)

DHS <- DHS %>% 
   mutate(SexPartnersLifetime_Cat = case_when
                               (SexPartners_Lifetime == "0" ~ "0",
                                SexPartners_Lifetime == "1" 
                                |SexPartners_Lifetime == "2" ~ "1-2",
                                SexPartners_Lifetime == "3" 
                                  |SexPartners_Lifetime == "4" 
                                  | SexPartners_Lifetime == "5"
                                  | SexPartners_Lifetime == "6"
                                  | SexPartners_Lifetime == "7" 
                                  | SexPartners_Lifetime == "8"
                                  | SexPartners_Lifetime == "9"
                                  | SexPartners_Lifetime == "10"
                                  | SexPartners_Lifetime == "11"
                                  | SexPartners_Lifetime == "12"
                                  | SexPartners_Lifetime == "13"
                                  | SexPartners_Lifetime == "15"
                                  | SexPartners_Lifetime == "16"
                                  | SexPartners_Lifetime == "17"
                                  | SexPartners_Lifetime == "18"
                                  | SexPartners_Lifetime == "20"
                                  | SexPartners_Lifetime == "25"
                                  | SexPartners_Lifetime == "30"
                                  | SexPartners_Lifetime == "38"
                                  | SexPartners_Lifetime == "45"
                                  | SexPartners_Lifetime == "59"
                                  | SexPartners_Lifetime == "95+" ~ "3+", 
                                 SexPartners_Lifetime == "Don't know" ~ "Don't Know"))

class(DHS$SexPartnersLifetime_Cat)

DHS$SexPartnersLifetime_Cat<-as.factor(DHS$SexPartnersLifetime_Cat)
# Check it:
table(DHS$SexPartners_Lifetime, DHS$SexPartnersLifetime_Cat)

#Remove the 28 "don't know"
DHS<-DHS %>% 
  filter(SexPartnersLifetime_Cat != "Don't Know")

DHS$SexPartnersLifetime_Cat<- factor(DHS$SexPartnersLifetime_Cat, levels = c("0", "1-2", "3+"))
levels(DHS$SexPartnersLifetime_Cat)
```
## STI in the last 12 months
```{r}
#Check missing values for STI in the last 12 months variable
sum(is.na(DHS$STI_12Months))
#no missing values

#Check class and levels for STI in the last 12 months variable
class(DHS$STI_12Months)
levels(DHS$STI_12Months)
summary(DHS$STI_12Months)

#drop the one "don't know" case
DHS<-DHS %>%
  filter(STI_12Months!= "Don't know")

# get rid of empty "don't know category
DHS$STI_12Months<-factor(DHS$STI_12Months)

levels(DHS$STI_12Months)
```
## Current Contraceptive Method
```{r}
#Check missing values 
sum(is.na(DHS$ContraceptiveMethod_Current))
#no missing values

#Check class and levels for contraceptive method
class(DHS$ContraceptiveMethod_Current)

summary(DHS$ContraceptiveMethod_Current)

#Make contraceptive method categorical and check it
DHS <- DHS %>% 
   mutate(ContraceptiveMethod_Cat = case_when
                               (ContraceptiveMethod_Current == "Male condom"
                                 |ContraceptiveMethod_Current == "Female condom" ~ "Condoms",
                                ContraceptiveMethod_Current == "Not using" ~ "Not Using",
                                ContraceptiveMethod_Current == "Pill" 
                                  | ContraceptiveMethod_Current == "IUD"
                                  | ContraceptiveMethod_Current == "Injections"
                                  | ContraceptiveMethod_Current == "Female sterilization" 
                                  | ContraceptiveMethod_Current == "Male sterilization"
                                  | ContraceptiveMethod_Current == "Periodic abstinence"
                                  | ContraceptiveMethod_Current == "Withdrawal"
                                  | ContraceptiveMethod_Current == "Implants/Norplant"
                                  | ContraceptiveMethod_Current == "Emergency contraception"
                                  | ContraceptiveMethod_Current == "Injections 2 month" ~ "Other Contraceptive"))
DHS$ContraceptiveMethod_Cat<-as.factor(DHS$ContraceptiveMethod_Cat)
table(DHS$ContraceptiveMethod_Cat, DHS$ContraceptiveMethod_Current)
summary(DHS$ContraceptiveMethod_Cat)
```
## Visited a health facility in the last 12 months
```{r}
#Check missing values 
sum(is.na(DHS$HealthFacility_12Months))
#no missing values

#Check class and levels for visit to health facility
class(DHS$HealthFacility_12Months)

summary(DHS$HealthFacility_12Months)
```
## Radio
```{r}
#Check missing values 
sum(is.na(DHS$Radio))
#no missing values

#Check class and levels for radio
class(DHS$Radio)

summary(DHS$Radio)

#Remove cases that are not dejure residents (114 cases)
DHS<-DHS %>% 
  filter(Radio != "Not a dejure resident")
#Remove empty "not a dejure resident" category
DHS$Radio<-factor(DHS$Radio)

levels(DHS$Radio)
summary(DHS$Radio)
```
## TV
```{r}
#Check missing values 
sum(is.na(DHS$TV))
#no missing values (probably because dropped the "not a dejure resident" cases for the Radio variable)

#Check class and levels for TV
class(DHS$TV)

summary(DHS$TV)

DHS$TV<-factor(DHS$TV)
levels(DHS$TV)
```
## Mobile Phone
```{r}
#Check missing values 
sum(is.na(DHS$MobilePhone))
#no missing values

#Check class and levels for Mobile Phone
class(DHS$MobilePhone)

summary(DHS$MobilePhone)
```
## Internet Use
```{r}
#Check missing values 
sum(is.na(DHS$InternetUse))
#no missing values

#Check class and levels for InternetUse
class(DHS$InternetUse)

summary(DHS$InternetUse)

## Make binary
#Make contraceptive method categorical and check it
DHS <- DHS %>% 
   mutate(InternetUse_Cat = case_when
                               (InternetUse == "Never" ~ "Never",
                                 InternetUse == "Yes, last 12 months"
                                 |InternetUse == "Yes, before last 12 months" ~ "Yes"))
DHS$InternetUse_Cat<-as.factor(DHS$InternetUse_Cat)
 #check if it categorized right
table(DHS$InternetUse_Cat,DHS$InternetUse)
```

#Prepare variable set for regression modeling
```{r}
# Check for missing data

#Choose only necessary vars and remove rows with missing data
CompleteDHS <- DHS %>%
  dplyr::select(HIVTest_LastYear, ResidenceType, Age, Age_Cat, Education_Cat, WealthIndex_Cat, MaritalStatus_Cat, Births_Last5Years_Cat, SexPartnersLifetime_Cat, STI_12Months, ContraceptiveMethod_Cat, HealthFacility_12Months, InternetUse_Cat, Radio, TV, MobilePhone, Individual_Weight, Cluster, Stratum) %>%
  drop_na()


MissingRate <-  1- nrow(CompleteDHS)/nrow(DHS)
#Look at missing rate
MissingRate
# Not missing any data
```
#Create Interaction Term
```{r}
#create interaction term to test linearity
CompleteDHS <- CompleteDHS %>%
  mutate(Age_times_logAge = Age * log(Age)) 
```

#Weight variable calculated 
```{r}
#Create weighted variable

CompleteDHS$Weight <- CompleteDHS$Individual_Weight/1000000

# Verify 
names(CompleteDHS)

#Create new var "svydesign" to assign weights for analysis
DHSdesign <- svydesign(id = ~Cluster, strata=~Stratum, weights = ~Weight, data=CompleteDHS)

#Check unweighted contninuous age variable
table(CompleteDHS$Age)

#Check continuous age weighted Frequencies
svytable(~Age, design=DHSdesign)
```
## Boxplots 
```{r}
#Boxplot to assess differences in HIV test by Age (weighted)

svyboxplot(Age~HIVTest_LastYear,design=DHSdesign,col =
             c("mistyrose","powderblue"), xlab="HIV Test", 
                ylab= "Age (years)")

#The median age of participants who never got a HIV test is lower compared to those who got a HIV test. 

#Compare with unweighted boxplots
DHS %>% 
  ggplot(aes(x= HIVTest_LastYear, y = Age)) +
  geom_boxplot(aes(fill =HIVTest_LastYear)) + 
  labs(x = "HIV Test Uptake", y = "Age (years)") + 
  theme_bw()
```
# Univariate Analysis
```{r}
#Run univariate anaysis (binomial logistic regression) using dependent variable (HIVTest) with each independent variable - Variables with statistical signficance satisfy the inclusion criteria for the multivariate logistic regression

lapply(c("ResidenceType", "Age_Cat","Education_Cat", 
         "WealthIndex_Cat", "MaritalStatus_Cat", 
         "Births_Last5Years_Cat", "SexPartnersLifetime_Cat", 
        "STI_12Months",
         "ContraceptiveMethod_Cat","HealthFacility_12Months", 
         "Radio", "TV","MobilePhone","InternetUse_Cat"),
       function(var) {
           formula    <- as.formula(paste("HIVTest_LastYear ~", var))
           univariateCheck <- svyglm(formula, data = DHS, family = binomial, 
                                design=DHSdesign )
           summary(univariateCheck)
       })
#Statistically Significant Variables (P>.05):
#Age_Cat
#MaritalStatus_Cat -"Partnered"
#Birth_Last5Years_Cat -"2+"
#SexPartnersLifetime_Cat
#ContraceptiveMethod_Cat
#HealthFacility_12Months
#MobilePhone

#Non-statistically significant Variables (P<.05)
#Residence_Type, Education, WealthIndex_Cat, STI_Months12, ContraceptiveMethod_Cat, Radio, TV, InternetUse_Cat

#Decision - Include all statistically significant variables (except "FirstSexAge_Cat) in the multivariate analysis. 

#Include the main exposure (ResidenceType), and the following covariates: contraceptive method, mobile phone ownership

#Even though we have non-statistically significant findings at the univariate level, the literature emphasizes the importance to include these variables for  predictive modeling

#Variables will be excluded from the final model if they do not improve model fit
```
# Test linearity assumption
```{r}
#Linearity - assess whether age as a continuous variable is appropriate for the regression models

boxTidwellAGE <- survey::svyglm(HIVTest_LastYear ~ Age + Age_times_logAge, data = CompleteDHS, family = "binomial", design = DHSdesign)

summary(boxTidwellAGE) #interaction term has a p value <0.05 - linearity assumption is violated. Use age categorical variable
```
# Binomial regression
```{r}
#Run logistic regression model
HIVLogitWGHT1<-svyglm(HIVTest_LastYear ~ ResidenceType + Age_Cat+ MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months, data =CompleteDHS, family = "binomial", design=DHSdesign)

ORHIVWGHT1<-exp(cbind(OR = coef(HIVLogitWGHT1), confint(HIVLogitWGHT1))) 
ORHIVWGHT1
```
# Test Assumptions
```{r}
#Assess multicollinearity
vif(HIVLogitWGHT1)
#All variables have a VIF values less than 5 - Assumption is met (no collinearity)

#Cook's D cutoff = 4/2798 
cutoff <- 0.00143

#Influential cases- Cook's D plot [Note: need to run both lines in one setting]
plot(HIVLogitWGHT1, which=4, id.n=5, col= "red")
abline(h=cutoff, lty=2, col="darkred")

#There are 98 influential cases

#identify obs with a Cook's distance greater than the cutoff
obs_no <- as.data.frame(cooks.distance(HIVLogitWGHT1)) %>%
  mutate(obs_no=row_number()) %>%
  filter(`cooks.distance(HIVLogitWGHT1)` > cutoff)

#Exlcude values in the Cook's D plot and compare models
Data_caseremov<-CompleteDHS %>% 
  mutate(CooksD = cooks.distance(HIVLogitWGHT1)) %>% 
  filter(CooksD < cutoff)

#Binomial logistic Regression with influential cases removed
HIVLogitWGHT2<-svyglm(HIVTest_LastYear ~ ResidenceType + Age_Cat+ MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months, data =Data_caseremov, family = "binomial", design=DHSdesign)

ORHIVWGHT2<-exp(cbind(OR = coef(HIVLogitWGHT2), confint(HIVLogitWGHT2))) 
ORHIVWGHT2

#Compare coefficients between models with and without influential observations 
compareCoefs(HIVLogitWGHT1, HIVLogitWGHT2)
#No changes detected, so we can leave all of the cases. 
```
# Run final parsimonious model
```{r}
#Run two logistic regression models 
#Model 1
HIVLogitWGHTPars1<-svyglm(HIVTest_LastYear ~  ResidenceType + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months, data =CompleteDHS, family = "binomial", design=DHSdesign)

summary(HIVLogitWGHTPars1)

ORHIVWGHTPars1<-exp(cbind(OR = coef(HIVLogitWGHTPars1), confint(HIVLogitWGHTPars1))) 
ORHIVWGHTPars1

#Model 2 - include contraceptive method and mobilephone ownership
HIVLogitWGHTPars2<-svyglm(HIVTest_LastYear ~ ResidenceType + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat  + ContraceptiveMethod_Cat+ HealthFacility_12Months + MobilePhone,data =CompleteDHS, family = "binomial", design=DHSdesign)

summary(HIVLogitWGHTPars2)

ORHIVWGHTPars2<-exp(cbind(OR = coef(HIVLogitWGHTPars2), confint(HIVLogitWGHTPars2))) 
ORHIVWGHTPars2

#Pseudo R Squares/Adjusted R Squares
fit.svyglm(HIVLogitWGHTPars1)
fit.svyglm(HIVLogitWGHTPars2)

anova(HIVLogitWGHTPars1, HIVLogitWGHTPars2)

anova(HIVLogitWGHTPars1, HIVLogitWGHTPars2, method="Wald")

AIC(HIVLogitWGHTPars1, HIVLogitWGHTPars2)
BIC (HIVLogitWGHTPars1, HIVLogitWGHTPars2, maximal = HIVLogitWGHTPars2)

#AIC and BIC values for model 1 is lower. This suggests that model 1 is a better fit. 
```
# Odds Ratios Graphic
```{r}
#Extract ORs 
boxLabels = c ("Residence (Urban)", "Age (18-20)", "Age (21-24)", "Marital Status (Not Partnered)", "Marital Status (Partnered)", "Births Last 5 Years (1)", "Births Last 5 Years (2+)", "Sex Partners (1-2)", "Sex Partners (3+)", "Healthcare Visits")
df <- data.frame(yAxis = length(boxLabels):1,
  boxOdds = 
   c(0.9288436, 1.6144059, 2.3996796, 1.1598624, 1.0144343, 
     1.0398193, 0.6681540, 1.9157983, 1.5951423, 1.1073606), 
  boxCILow = 
   c(0.7690751, 1.1783163, 1.7264368, 0.3789230, 0.728314, 
     0.8000482, 0.3920753, 1.4012436, 1.1160488, 0.8622075),
  boxCIHigh = 
  c(1.1218026, 2.2118902, 3.3354605, 3.5502749, 1.4129566, 
    1.3514487, 1.1386328, 2.6193042, 2.2798996, 1.4222185))


#create plot 
(p <- ggplot(df, aes(x = boxOdds, y = boxLabels)) +
  geom_vline(aes(xintercept = 1), size = .25, linetype = 'dashed') +
  geom_errorbarh(aes(xmax = boxCIHigh, xmin = boxCILow), size = .5, height = 
      .2, color = 'gray50') +
  geom_point(size = 3.5, color = 'orange') +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor =    
  element_blank ()) +
  scale_x_continuous(breaks = seq(0,7,1) ) +
  coord_trans(x = 'log10') +
  ylab('') +
  xlab('Odds ratio (log scale)') +
  ggtitle('ODDS RATIOS - Binomial Regression Model')
)
```
# Table 1
```{r}
#Label variables
label(CompleteDHS$HIVTest_LastYear)<-"HIV Test Within Last Year"
label(CompleteDHS$Age_Cat)<-"Age (Years)"
label(CompleteDHS$Education_Cat)<-"Education Level"
label(CompleteDHS$WealthIndex)<-"Wealth Index"
label(CompleteDHS$MaritalStatus_Cat)<-"Marital Status"
label(CompleteDHS$Births_Last5Years_Cat)<-"Births in Last 5 Years"
label(CompleteDHS$SexPartnersLifetime_Cat)<-"Lifetime Sex Partners"
label(CompleteDHS$STI_12Months)<-"STI in Last 12 Months"
label(CompleteDHS$ContraceptiveMethod_Cat)<-"Contraceptive Method"
label(CompleteDHS$HealthFacility_12Months)<-"Visited Healthcare Facility in Last 12 Months"
label(CompleteDHS$InternetUse_Cat)<-"Internet Access"
label(CompleteDHS$Radio)<-"Radio Access"
label(CompleteDHS$TV)<-"Television Access"
label(CompleteDHS$ResidenceType)<-"Residence Type"

#Make table
table1(~HIVTest_LastYear + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat + SexPartnersLifetime_Cat + HealthFacility_12Months|ResidenceType, overall = "Total", rowlabelhead="Variable", CompleteDHS)
```
# Figure 1
```{r}
#The DHS dataset is 8514 observations when it is read in. After we select only women ages 15-24, the dataset is 2913 observations. If we exclude those who answered "don't know" to the number of lifetime sex partners (28), then the dataset is 2885. Drop 1 more who answered "don't know" to STI question, leaving 2884. Remove 113 who are not dejure residents, leaving 2771. Did not exclude 98 influential cases because it did not matter to the model.

grViz("digraph flowchart {
      node [fontname = Helvetica, shape = rectangle, fontsize=10] 
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
    
      
      tab1 -> tab2 -> tab3 -> tab4 -> tab5}
      [1]: 'DHS dataset including all women n=8,514'
      [2]: 'Excluding 5,601 participants not ages 15-24 n=2,913'
      [3]: 'Excluding 28 individuals who did not know number of lifetime sex partners n = 2,885'
      [4]: 'Excluding 1 individual who did not know about STI in the last 12 months n = 2,884'
      [5]: 'Excluding 113 individuals who were not dejure residents n = 2,771'
      ")
```
# Test whether wealth index is an effect modifier
```{r}
#Model 1 (with wealth index added)
HIVLogitWGHTWealth<-svyglm(formula =HIVTest_LastYear ~  ResidenceType + WealthIndex_Cat + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months, data =CompleteDHS, family = "binomial", design=DHSdesign)

summary(HIVLogitWGHTWealth)

ORHIVWGHTWealth<-exp(cbind(OR = coef(HIVLogitWGHTWealth), confint(HIVLogitWGHTWealth))) 
ORHIVWGHTWealth

# model with wealth index * residence type interaction term
HIVLogitWGHTinteraction <- svyglm(HIVTest_LastYear ~  ResidenceType + WealthIndex_Cat + Age_Cat + MaritalStatus_Cat + Births_Last5Years_Cat+ SexPartnersLifetime_Cat + HealthFacility_12Months + ResidenceType*WealthIndex_Cat, data =CompleteDHS, family = "binomial", design=DHSdesign)

summary(HIVLogitWGHTinteraction)

ORHIVLogitWGHTinteraction<-exp(cbind(OR = coef(HIVLogitWGHTinteraction), confint(HIVLogitWGHTinteraction))) 
ORHIVLogitWGHTinteraction

#Interaction Test
anova(HIVLogitWGHTWealth,HIVLogitWGHTinteraction, test = "F", method = "LRT")
#p>0.05,Interaction term is not significant

#Plot interactions
#install.packages("interactions")
library(interactions)

#use cat_plot to plot the interactions

#Visualization 1
cat_plot(HIVLogitWGHTinteraction, pred = ResidenceType, modx = WealthIndex_Cat, 
         geom = "point",
         x.label = "Area of Residence", y.label = "HIV Test in Last Year", legend.main = "Wealth Index")
#No interaction 
```
